\documentclass[margin, 11pt]{res}

% \usepackage{feynmf}
\usepackage[usenames, dvipsnames]{color}
\usepackage{amsmath}
\usepackage{hyperref}

\usepackage{fontspec}

\usepackage[T1]{fontenc}
\usepackage[usefilenames,RMstyle={Text,Semibold},SSstyle={Text,Semibold},TTstyle={Text,Semibold},DefaultFeatures={Ligatures=Common}]{plex-otf} %
\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif

% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\pagenumbering{gobble}

\definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
\definecolor{cobalt}{rgb}{0.0, 0.28, 0.67}
\definecolor{blue(pigment)}{rgb}{0.2, 0.2, 0.6}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\definecolor{coolblack}{rgb}{0.0, 0.18, 0.39}
\hypersetup{colorlinks=true, urlcolor=darkcerulean}

\newcommand{\li}{https://linkedin.com/in/harishvadaparty}
\newcommand{\gh}{https://github.com/Harryalways317}
\newcommand{\personalsite}{https://hvadaparty.vercel.app}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\newsectionwidth{1in}




\newcommand{\resumeSubheading}[4]{

\begin{tabular*}{1.01\textwidth}{@{\hspace{-4pt}}l @{\extracolsep{\fill}} r}
\textbf{#1} & #2 \\
      {#3} &  {#4}
\end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubSubheading}[2]{
\begin{tabular*}{1.01\textwidth}{@{\hspace{-4pt}}l @{\extracolsep{\fill}} r}
    #1 & #2 
\end{tabular*}\vspace{-7pt}
}

% if using pdflatex:
% \setlength{\pdfpagewidth}{\paperwidth}
% \setlength{\pdfpageheight}{\paperheight}
%
\newenvironment{list1}{
	\begin{list}{\ding{113}}{%
		\setlength{\itemsep}{0in}
		\setlength{\parsep}{0in} \setlength{\parskip}{0in}
		\setlength{\topsep}{0in} \setlength{\partopsep}{0in}
		\setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
	\begin{list}{$\bullet$}{%
	    \small
		\setlength{\itemsep}{0in}
		\setlength{\parsep}{0in} \setlength{\parskip}{0in}
		\setlength{\topsep}{0in} \setlength{\partopsep}{0in}
		\setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{
	{\Huge \scshape Harish Vadaparty}
	\vspace{2pt}
	}
\address{
%    \small +91-6301786793 $|$
    \href{https://hvadaparty.vercel.app}{Portfolio} $|$
    \href{mailto:harishvadapartygmail.com}{harishvadaparty@gmail.com} $|$ 
    \href{\li}{linkedin.com/in/harishvadaparty} $|$
    \href{\gh}{github.com/Harryalways317}
}

\begin{resume}
% \section{\sc Contact Information}
% \vspace{.05in}
% \begin{tabular}{@{}p{3.17in}p{4in}}
% 	\href{\li}{linkedin.com/in/jakegut} & \href{\gh}{github.com/jakegut}\\
%     \href{mailto:jakegut0108@gmail.com}{jakegut0108@gmail.com} & \href{\personalsite}{jakegut.com}\\
%      (979) 676-3030
%     %  (123) 456-7890
%         % & Available to start from Nov 1st\\
% \end{tabular}

\section{\sc Work Experience}

\vspace{2pt}

\resumeSubheading{{\bf OnFinance.ai}}{Bangalore, IN}
{Backend and AI Engineer}{Apr. 2024 -- Present}

\begin{list2}
    \item{Led the backend team, working with a cross-tech stack of GCP, Azure, Golang, and Python, powering Gen AI applications and advanced Copilots.}
    \item{Built and optimized data processing pipelines with queue-based systems, achieving a 70\% increase in document processing speed, supporting text, audio, and video data.}
    \item{Developed a bulk scraping pipeline for company data collection, now integral to our company data analytics operations.}
    \item{Developed and maintained Copilot backends for production clients like Oister and Avendus, ensuring seamless performance and scalability.}
    \item{Implemented RAG workflows and advanced retrieval mechanisms, enabling agentic search and structured data extraction from financial documents.}
    \item{Designed a template-based backend system, reducing client onboarding time by 50\%.}
    \item{Created centralized services for LLM inferencing, log management, and error monitoring to improve system reliability.}
    \item{Led DevOps efforts, including resource management, CI/CD pipelines, and infrastructure setup, with centralized logging and usage analytics integrations.}
    \item{\textbf{Tech Stack:} Python, Golang, Java, MongoDB, PostgreSQL, Kafka, Docker, Azure, GCP.}
\end{list2}

\resumeSubheading{{\bf Hexon Labs}}{Bangalore, IN}
                 {Software Engineer, Backend and Data}{Jul. 2022 -- Apr. 2024}

\begin{list2}
\item {Led fine-tuning of large language models (LLMs) for Alignment with DPO and implemented AI-driven solutions on customer usecases.}
\item {Developed and deployed Formless AI, a platform for AI-prompt-based form creation and interactive data collection, streamlining surveys and form data collection into a interesting way.}
\item {Engineered AI agents for competition analysis, metrics collection and automated report generation, providing actionable insights and improving decision-making.}
\item {Led backend development for a grocery application using AWS, Node.js, Python, and TypeScript, integrating ElasticSearch to improve search relevancy by 60\% and building a recommendation engine that increased relevant cart items by 40\%.}
\item {Developed service applications for notifications, delivery management, and reporting, and ensured real-time synchronization across services data with CDC for inventory, pricing, and store POS systems.}
\item {Implemented RAG-LLM workflows in-app and worked with Tortoise TTS for voice cloning and audio-based lip sync, enhancing the overall user experience with AI.}
\end{list2}



\resumeSubheading{{\bf Board Infinity}}{Mumbai, IN}
                 {Software Engineer Intern}{March 2022 -- June. 2022}
                 
\begin{list2}
\item{Contributed to an established Ed Tech application in rewrite from React Native to Flutter with MVVC}
\item{Developed multiple features on LMS, Blogs, Event and Course Management}
\item{Implemented UXCam for analytics and notifications pipeline for FCM and Imrpoved animations}
\item{Rewrote Modules of the app by caching and data reuse which improved performance by 40\%}
\end{list2}

% \vspace{0.15in}
\section{\sc Education}

\vspace{2pt}

\resumeSubheading{Lendi Institute of Engineering and Techonology}{Vizianagaram, IN}
             {Bachelor of Techonology in Computer Science}{June 2022}

\section{\sc Projects}

\resumeSubSubheading{\textbf{Any2Any Convertor}}
{Python, Flask, RabbitMQ, MySQL,MongoDB}

\begin{list2}
\item {Developed an OCR conversion, MP3 extraction and File conversion service with support for pdf to docx/docx to pdf.}
        \item {Implemented a Gateway for handling authentication, file storage, and processing requests in a queue with parallel workers.}
        \item {Established an email notification system to inform users upon completion of file processing.}
        \item {Encapsulated the service in a Kubernetes (K8s) environment for scalability, supporting various conversions and Volume Persistance on failures.}
\end{list2}

\resumeSubSubheading{\textbf{Job Leads Generator and Staffing Assistant}}
{Python,Open AI API,Langchain,Postgres}

\begin{list2}
        \item Created an end-to-end automated system for identifying potential leads and generating emails.
        \item Developed web scrapers to extract and clean data about companies with active hiring needs.
        \item Integrated Langchain \& OpenAI to create personalized email templates based on the scraped data, enhancing outreach for staffing services.
\end{list2}

\resumeSubSubheading{\textbf{CurateSphere - A News Summarizer Platform}}
{Python,Fast API,Open AI,Postgres,Qdrant}

\begin{list2}
    \item Developed a comprehensive news summarization platform, CurateSphere, capable of condensing news articles into concise summaries of under 5 minutes reading time.
    \item Implemented a robust system for scraping and ingesting news content from diverse sources, utilizing Qdrant for storing article embeddings and appending succinct summaries (TLDR) to each article.
    \item Ranks news articles on a priority basis and selects top 10 articles based on score generated and summarizes them as top news.
\end{list2}

\resumeSubSubheading{\textbf{Data Processing Service}}
{Python, Azure, OCR, LLM, PostgreSQL}

\begin{list2}
    \item Developed a comprehensive data processing service supporting documents, audio, and LLM utilities.
    \item Built functionality to upload documents to Azure, perform OCR, reconstruct tables, and chunk content into context-aware sections for vector processing.
    \item Implemented optional question generation on document chunks to enhance RAG in chat applications.
    \item Integrated audio data transcription and embedding generation for audio-based RAG, improving the accuracy of information retrieval.
    \item Developed tools for structured data extraction and entity recognition to facilitate precise information processing.
    \item Designed an ODM parser enabling agentic retrieval of data from databases, streamlining complex queries.
\end{list2}

\resumeSubSubheading{\textbf{Spot Instance Manager}}
{Python, Fast API, PostgreSQL, boto3 sdk}

\begin{list2}
    \item Created a minimalist Spot Manager Application that manages spot instances from AWS with auto stop and auto start features.
    \item Implemented a inferencing proxy for deployed models with VLLM that allocates a spot instance with desired AMI from existing pool of instances and start new instances based on availability
    \item Uses boto sdk for getting details, status of instanaces and availability group and fleet allocation and synced it with local postgres and redis
    \item Added functionality for supporting multiple AMI and instance types and fetching instance types from config file under single zone
    \item Added multiple background cron jobs to stop unused instances and continous data sync between instance pool
\end{list2}


\section{\sc Technical Skills}

\textbf{Languages}{: Python,JavaScript/TypeScript, Go, Dart, Java, C/C++} \\
\textbf{Frameworks}{: Flutter, Node.js, Flask, FastAPI, Express} \\
\textbf{Tools}{: PostgreSQL, Redis, MongoDB, Elastic Search, AWS} 

\section{\sc Certifications}
\textbf{AWS Certified Cloud Practitioner - Validation Number}{: WL78T7D25MQQ1C30} \\

\vspace{0.2in}

\end{resume}
\end{document}
